---
title: 'Statistical report: Cardiac resynchronization therapy practice in heart failure vs. electrophysiology settings/clinics in Europe'
subtitle: 'DRAFT'
author: 'Statistician: Lina Benson'
  
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    number_sections: yes
link-citations: yes
bibliography: references.bib
nocite: '@*'
header-includes:
   - \usepackage{draftwatermark}
---

\newpage 
\tableofcontents 
\listoftables
\listoffigures
\newpage


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, include = TRUE, comment = "",
  warning = FALSE, message = FALSE, fig.pos = "H",
  fig.path = "../output/figs/"
)
options(knitr.kable.NA = "")
```

```{r adjust_directory_if_needed, include=FALSE}
# Uncomment lines below if rmd file is placed in a subdirectory
knitr::opts_knit$set(root.dir = normalizePath("../"))
```

```{r load_project}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and code in lib directory

ProjectTemplate::reload.project()

cacheon <- TRUE
```             

# Data handling

## Data sources
### CRT Survey II

General analysis population is used.

### ESC registry

hf3_lt_fu_data_soladis_jan19.sas7bdat (from the folder DATABASE_ANALYZED.ZIP). 

### SwedeHF registry

SHFDB3, https://kiheartfailure.github.io/shfdb3/, v 3.2.3. 

## Inclusion/exclusion criteria

```{r flow}
default_kable(flow, caption = "Flowchart", scale_down = F)
```  

```{r overalldescstat}
tab1overall <- print(
  CreateTableOne(
    vars = c("age", "sex"),
    data = data3,
    strata = "data"
  ),
  smd = FALSE,
  missing = FALSE,
  printToggle = FALSE,
  nonnormal = "age",
  test = FALSE,
  catDigits = 0,
  contDigits = 0,
  explain = TRUE,
  noSpaces = TRUE,
  showAllLevels = TRUE
)
tab1overall <- as_tibble(cbind(Variable = rownames(tab1overall), tab1overall))
names(tab1overall) <- c("Variable", "", "CRT Survey II", "ESC Registry", "SwedeHF Registry")

default_kable(tab1overall, caption = "Overall stats", scale_down = F)
```  

## Created variables 

The information needed to derive the MAGGIC score was not available in all 3 registries. 
In those cases the same assumption was made in all 3 registries, irrespectively 
if the information was collected in order to make the 3 comparable. 
The following assumptions were made: EF <30% gives 6 points and EF 30-39% gives 3 points. 
All patients are considered non-smokers and all patients have been assumed to 
have a duration of HF > 1.5 years.  

# Statistical analysis 

## General

All analyses were performed using `r sessionInfo()$R.version$version.string` [@r]. 
The level of significance is set to 5%, two-sided. No adjustment for multiple 
comparisons were made and therefore the results should be viewed with some care.

## Sensitivity analyses

A comparison is also performed for overlapping countries between the 3 registries where 
the countries that are in CRT Survey II and ESC Registry or SwedeHF are included. 
The main analysis is considered to be the one with all countries. 

## Baseline characteristics

```{r, child = "../src/tab1.Rmd"}

```

```{r, child = "../src/tabcrtesc.Rmd"}

```

```{r, child = "../src/tabcountry.Rmd"}

```

\clearpage

```{r, child = "../src/bar.Rmd"}

```

\clearpage

```{r, child = "../src/map.Rmd"}

```

\clearpage

## Predictors of CRT use

### Missing data

Missing data was imputed with multiple imputation (n = 10) using mice [@mice]. 
Variables included in the model are the same as are included in the logistic regression models. 
Imputation was done separately for the two registries.  

### Assumptions

Outliers were investigated with Cook's distance and multicollinearity 
with the variance inflation factor in the full model in the overall population.
=> No action deemed necessary. 

```{r, child = "../src/predcrt.Rmd"}

```

\clearpage

## Outcomes after CRT

```{r, child = "../src/km.Rmd"}

```

\clearpage

# Reproducibility

## R session information {#sessioninfo}

```{r sessinfo}
sessionInfo()
```

## R code

The R code for all data handling and statistical analyses are found: 
https://github.com/KIHeartFailure/crt. On publication
the repository will be made public so as to 
link to it from the resulting article for increased transparency and code sharing.
No data or output is stored in the repository. 

# References
